### 2022-09-19 Thesis/text/implementierung.tex
implementation chapter almost finished, validation chapter tomorrow

The system supervisor component is partly outsourced into a component outside of the thread of the BT, because of the same reasons as the sensor backup component discussed in the previous section. The synchronous executor would stop the execution of the whole behavior tree, which is why the component needs to be moved inside of a new thread. The system supervisor, nachfolgend also called execution checker, is receiving messages from nodes that are not implemented as ROS2 lifecycle nodes. If a node stops sending messages or stops responding completely the external execution checker can inform the BT via a provided service of a problem with the node. ROS2 lifecycle nodes provide information about their health via an implementation of a FSM inside of the node. The current node state can be found out via a service call. However, to ensure the node is working correctly the output of the node needs to be checked too, because it might be that the FSM inside of the node did not pick up on a error. 
The system supervision is constantly checking the system's health. The BT is using service calls to get the health information about the compononts which are checked inside of Condition Nodes. 
The components get checked by the BT inside of a Fallback. If the condition for the execution is met, the Condition Node returns "success" and the fallback would exit to move on to the next fallback and execution condition check (see fig. xx). In case the execution checker detects a node failure, a sequence to react to the sensor failure is executed in which the robot slows down to a minimum and tries to restart the sensor. Should the restart fail the robot will not be able to navigate in a safe manner anymore and will come to a complete stop. This behavior pattern is realized for the lidar, the IMU and the wheel odometry.

@@

Figure for the Collision Behavior from Groot.

@@

Regarding the map reset, we have to determine if we are creating a new map with a SLAM method or if the map server provided a previously saved map. 
In case of the running SLAM, the map needs to be reset to before the collision occurred.

@@

@@

>>>>

The system supervisor component is partly outsourced into a component outside of the thread of the BT, because of the same reasons as the sensor backup component discussed in the previous section. The synchronous executor would stop the execution of the whole behavior tree, which is why the component needs to be moved inside of a new thread. The system supervisor, nachfolgend also called execution checker, is receiving messages from nodes that are not implemented as ROS2 lifecycle nodes. If a node stops sending messages or stops responding completely the external execution checker can inform the BT via a provided service of a problem with the node. ROS2 lifecycle nodes provide information about their health via an implementation of a FSM inside of the node. The current node state can be found out via a service call. However, to ensure the node is working correctly the output of the node needs to be checked too, because it might be that the FSM inside of the node did not pick up on a error. 
The system supervision is constantly checking the system's health. The BT is using service calls to get the health information about the compononts which are checked inside of Condition Nodes. 
The components get checked by the BT inside of a Fallback. If the condition for the execution is met, the Condition Node returns "success" and the fallback would exit to move on to the next fallback and execution condition check (see fig. xx). In case the execution checker detects a node failure, a sequence to react to the sensor failure is executed in which the robot slows down to a minimum and tries to restart the sensor. Should the restart fail the robot will not be able to navigate in a safe manner anymore and will come to a complete stop. This behavior pattern is realized for the lidar, the IMU and the wheel odometry. \\

@@

\begin{figure}
	\includegraphics[width=1.0\textwidth]{images/collision_fallback.png}
	\caption{Collision Fallback Behavior}
\end{figure}

@@

The modification is done in the following manner

\textit{Formula for determining execution time}

Regarding the map reset, we have to determine if we are creating a new map with a SLAM method or if the map server provided a previously saved map. 
In case of the running SLAM, the recent updates to the map must be verwerfen to a map prior to when the collision occurred.
When a static map is provided by the map server component from Nav2 the map needs to be updated with a new obstacle at the point of collision and republished by the map server.

The activity of the "MapUpdateAfterCollision" action node is depicted in figure xx. The collision point is estimated by the robot's pose which refers to the robot base link and the robot footprint. We assumed that the collision point is right in front of the robot, because the local planner favours forward drive kinematics. The simulated bumper sensor can provide more nuanced information about the point of contact, but this functionality can not be achieved on a real robot with an IMU-based collsion detection, hence we simplified the obstacle position to always be in front of the robot. 
The collision position is calculated with

\textit{Formula here}

A 25 by 25 cm square with full occupation of that space is added to the current map and then saved to be reloaded by the map server as depicted in figure xx.

The original goal is then republished to replan the global path on the updated map.

In this manner obstacles lower than the lidar scan height can be detected. With this behavior the robot should also be able to eventually navigate around transparent obstacles which do not reflect the laser. Glass doors are known to cause issues for robots based only on lidars.

@@

The battery behavior has the goal to monitor the robot's battery and has to make to the decision if the robot should navigate to a new goal location or not. The decision is based on the current battery charge and the estimated consumption of energy to reach the new goal. The robot should not begin the navigation process if it is probable that the remaining charge will not suffice for the driving.

\begin{figure}
	\includegraphics[width=0.5\textwidth]{images/battery_fallback.png}
	\caption{Battery Fallback Behavior}
\end{figure}
The robot has to take into account the idle consumption, the energy to drive the motors. With this information we created a simple linear function for the energy expenditure to predict the required power depending on the length of the path. To make the algorithm fail safe, we added an additional safety factor into the function, to berücksichtigen the scenario where the robot has to reroute and drive a longer route or has to stop for a moment. The resulting function can be described as: \\

\textit{Formel here}

On a real robot the average values for the idle and driving consumption could be experimentally determined. For the simulated turtlebot we created a simulated battery package which updates the battery charge every second. The battery package subscribes to the comman velocity topic and decreases the battery charge for every message that is received. We created the battery package because the behavior for this scenario needs to be tested. This is way the consumption rates are not close to reality.
The battery package provides a service to get the battery charge and the values for the angenommenen consumption rates. The BT node "IsBatterySufficientCheck" calls the service to compare the current battery to the calculated consumption. The battery behavior fallback will cancel the navigation goal if the robot can not reach the given goal with the remaining charge. \\

@@

With this behavior, we implement a way to make the global planner more flexible. 
The execution checker component monitors the health of the Nav2 global planner. Additionally, the BT analyses the global planners output. If one of the condition fails, the given navigation goal is not reachable by the planning algorithm. We combat this by shifting the goal to a nearby alternative to get the robot as close to the original goal as possible. Is the location still unreachable, the goal gets moved further away and closer to the robot again. This routine gets repeated for up to ten times, which leads to a distance to the original goal of up to one meter. 
The goal gets moved on a straight vector towards the robot. Other strategies for finding alternative goals were not implemented in this behavior.

\begin{figure}
	\includegraphics[width=0.75\textwidth]{images/global_planning_fallback.png}
	\caption{Path Planning Fallback}
\end{figure}
